Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-04 Draft/definition.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

This process possesses three LO contributions of different orders.
At LO, this process can proceed via three different coupling-order combinations:
$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
The first, commonly referred to as EW contribution or VBS~\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
of vector bosons.}, receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
(center diagram) or from
triple-boson production (right diagram).
Note that $s$-, $t$-, and $u$-channel contributions are defined according to the quark lines.
$s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line.
$u$-channel refers to contributions with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state
The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.

@@

The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
radiated off the quark lines. Because of the different colour structure, this contribution features a 
different kinematical behaviour than VBS. Nonetheless they share the same final state, and this class of contributions therefore constitutes an irreducible background to the genuine VBS signal.

@@

In experimental measurements, special cuts, called VBS cuts, are designed to enhance the EW contribution over the QCD one and to suppress the interference.
These cuts are based on the different kinematical behaviour of the two contributions.
The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
The two $\PW$ bosons are mostly produced centrally.
This is in contrast to the QCD contribution which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
Note that, as pointed out in Ref.~\cite{Biedermann:2017bss}, when considering full amplitudes, the separation between EW and QCD production becomes ill
defined.
Hence, combined measurements which are better theoretically defined should be preferably performed by the experimental collaborations at the LHC.

>>>>

This process possesses three LO contributions of different orders.
At LO, this process can proceed via three different coupling-order combinations:
$\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas{2}\alpha^{4}\right)}$, and $\mathcal{O}{\left(\alphas\alpha^{5}\right)}$.
The first, commonly referred to as EW contribution or VBS,\footnote{The name VBS is used even though not all Feynman diagrams involve the scattering
of vector bosons.} receives the contributions from Feynman diagrams such as those in Fig.~\ref{diag:LO}:
in addition to genuine VBS contributions (left diagram), it also features $s$-channel contributions with non-resonant vector bosons 
(center diagram) or from
triple-boson production (right diagram).
Note that $s$-, $t$-, and $u$-channel contributions are defined according to the quark lines.
$s$-channel denotes all Feynman diagrams where the two initial-state partons are connected by a continuous fermion line.
$u$-channel refers to contributions with crossed fermion lines, which appears for identical quarks or anti-quarks in the final state
The $s$-channel contributions will play a particular role in the study of the various contributions in Sec.~\ref{subsec:contributions}.

@@

The second coupling combination corresponds to diagrams with a gluon connecting the two quark lines, and with the $\PW$ bosons 
radiated off the quark lines. Because of the different colour structure, this contribution features a 
different kinematic behaviour than VBS. Nonetheless they share the same final state, and this class of contributions therefore constitutes an irreducible background to the genuine VBS signal.

@@

In experimental measurements, special cuts, called VBS cuts, are designed to enhance the EW contribution over the QCD one and to suppress the interference.
These cuts are based on the different kinematical behaviour of the contributions.
The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
The two $\PW$ bosons are mostly produced centrally.
This is in contrast to the QCD contribution which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariant-mass cuts for the jets.
Note that, as pointed out in Ref.~\cite{Biedermann:2017bss}, when considering full amplitudes, the separation between EW and QCD production becomes ill
defined.
Hence, combined measurements which are better theoretically defined should be preferably performed by the experimental collaborations at the LHC.

### 2018-03-04 Draft/description.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

\begin{table*}[ht!]
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alphas \alpha^5)$  \\
        \hline
        \hline
        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
        {\sc Powheg}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
    \end{tabularx}
    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
\end{table*}

@@

\item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator written by Christopher Schwan and matrix elements taken from different sources:
Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
For the fiducial cross sections it uses the VBS approximation at LO and NLO.
The virtual corrections are additionally approximated using a double pole approximation.
For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) are used.

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, {\sc IREGI}~\cite{ShaoIREGI}, or {\sc Collier}~\cite{Denner:2016kdg}, together with an in-house 
        implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweighting
        at zero additional CPU cost~\cite{Frederix:2011ss}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme
> import model loop_qcd_qed_sm_Gmu
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD]
> output
\end{verbatim}
  With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
        with the current version of the code.}, finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
        For what concerns the virtual matrix element, because of some internal limitations which will be lifted in the future version capable of computing both QCD and EW corrections,
        only loops with QCD-interacting particles are generated. Such an approximation is equivalent to the assumption that the finite part of
        those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
        pole-cancellation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
        {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards\-/FKS\_\-params.dat} file to -1.

\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
It can compute arbitrary processes for the LHC at both NLO QCD and EW accuracy in the Standard Model.
This is made possible by the fact that {\sc Recola} can compute arbitrary processes at tree and one-loop level in the Standard Model.
To that end, it relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg} to numerically evaluate the one-loop scalar and tensor integrals.
In addition, the subtraction of the IR divergences appearing in the real corrections has been automatised thanks to the Catani--Seymour dipole formalism for both QCD and QED \cite{Catani:1996vz,Dittmaier:1999mb}.
The code has demonstrated its ability to compute at NLO high multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained from this tool.
One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}. 
In {\sc MoCaNLO+Recola} no approximation is performed at LO as well as at NLO, and, in particular, also contributions stemming from EW corrections to the interference are computed.

@@

  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw,Nason:2006hfa} is a framework for matching NLO-QCD calculations with parton showers.
It relies on the user providing the matrix elements and Born phase space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.

  \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
    parton-level Monte Carlo for processes with electroweak bosons. It
    allows the calculation of VBS processes at NLO QCD in the VBS
    approximation, with process IDs between 200 and 290. The corresponding
    s-channel contributions are available separately as tri-boson processes with
    semi-leptonic decays, with process IDs in the 400 range. These can simply
    be added on top of the VBS contribution, as interferences between the two are neglected.
    The usage of leptonic tensors in the calculation, pioneered in
    Ref.~\cite{Jager:2006zc}, thereby leads to a significant speed improvement over
    automatically generated code.  Besides the SM, also a variety of
    new-physics models including anomalous couplings of the Higgs and gauge
    bosons can be simulated.

  \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
      event generator with the LO matrix element generator {\sc O'Mega}. \ZM{ if NLO results for this processes cannot be provided, we should skip what follows, or at least clarify the limitations}
provides FKS subtraction terms for any NLO process, while virtual matrix
elements are provided externally by {\sc
OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
(cf. above) can be used as well). {\sc Whizard} allows to simulate a
huge number of BSM models as well, in particular for new physics in
the VBS channel in terms of both higher-dimensional operators as well as explicit
resonances.

@@

We conclude this section by summarising the details of the various codes in Tab.~\ref{tab:wg1_codes}. In particular, it is specified whether
\begin{itemize}
    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
    \item interferences between diagrams are included at LO;
    \item diagrams which do not feature two resonant vector bosons are included;
    \item the so-called non-factorisable (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
        the  $\mathcal O (\alpha^6$) term.
\end{itemize}

>>>>

@@

\item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator written by Christopher Schwan and matrix elements taken from different sources:
Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
For the fiducial cross sections it uses the VBS approximation at LO and NLO.
The virtual corrections are additionally approximated using a double-pole approximation.
For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) are used.

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, {\sc IREGI}~\cite{ShaoIREGI}, or {\sc Collier}~\cite{Denner:2016kdg}, together with an in-house 
        implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweighting
        at zero additional CPU cost~\cite{Frederix:2011ss}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme
> import model loop_qcd_qed_sm_Gmu
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD]
> output
\end{verbatim}
  With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electroweak corrections, it is not yet possible to compute such corrections
        with the current version of the code.}, finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
        For what concerns the virtual matrix element, because of some internal limitations which will be lifted in the future version capable of computing both QCD and EW corrections,
        only loops with QCD-interacting particles are generated. Such an approximation is equivalent to the assumption that the finite part of
        those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
        pole-cancellation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
        {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards\-/FKS\_\-params.dat} file to -1.

\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
It can compute arbitrary processes for the LHC at both NLO QCD and EW accuracy in the Standard Model.
This is made possible by the fact that {\sc Recola} can compute arbitrary processes at tree and one-loop level in the Standard Model.
To that end, it relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg} to numerically evaluate the one-loop scalar and tensor integrals.
In addition, the subtraction of the IR divergences appearing in the real corrections has been automatised thanks to the Catani--Seymour dipole formalism for both QCD and QED \cite{Catani:1996vz,Dittmaier:1999mb}.
The code has demonstrated its ability to compute at NLO high multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained thanks to this tool.
One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}. 
In {\sc MoCaNLO+Recola} no approximation is performed neither at LO nor at NLO.
It implies that, also contributions stemming from EW corrections to the interference are computed.

@@

  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw,Nason:2006hfa} is a framework for matching NLO-QCD calculations with parton showers.
It relies on the user providing the matrix elements and Born phase-space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.

  \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
    parton-level Monte Carlo for processes with electroweak bosons. It
    allows the calculation of VBS processes at NLO QCD in the VBS
    approximation, with process IDs between 200 and 290. The corresponding
    $s$-channel contributions are available separately as tri-boson processes with
    semi-leptonic decays, with process IDs in the 400 range. These can simply
    be added on top of the VBS contribution. Interferences between the two are therefore neglected.
    The usage of leptonic tensors in the calculation, pioneered in
    Ref.~\cite{Jager:2006zc}, thereby leads to a significant speed improvement over
    automatically generated code.  Besides the SM, also a variety of
    new-physics models including anomalous couplings of the Higgs and gauge
    bosons can be simulated.

  \item {\sc Whizard}~\cite{Moretti:2001zz,Kilian:2007gr} is a multi-purpose
      event generator with the LO matrix element generator {\sc O'Mega}. \ZM{ if NLO results for this processes cannot be provided, we should skip what follows, or at least clarify the limitations}
provides FKS subtraction terms for any NLO process, while virtual matrix
elements are provided externally by {\sc
OpenLoops}~\cite{Cascioli:2011va} (alternatively, {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}
(\emph{cf.}\ above) can be used as well). {\sc Whizard} allows to simulate a
huge number of BSM models as well, in particular in
the VBS channel in terms of both higher-dimensional operators as well as explicit
resonances.

@@

We conclude this section by summarising the characteristics of the various codes in Tab.~\ref{tab:wg1_codes}.
In particular, it is specified whether
\begin{itemize}
    \item all $s$- and $t/u$-channel diagrams are included;
    \item interferences between different diagrams of diagrams ($s/t/u$-channel) are included at LO;
    \item diagrams which do not feature two resonant vector-bosons are included;
    \item the so-called non-factorisable (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the interference of order $\mathcal O (\alpha^5\alphas)$ are included.
    These corrections are of the same order as the NLO QCD corrections to the contribution of order $\mathcal O (\alpha^6$) term.
\end{itemize}

\begin{table*}[ht!]
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Code  &  $\mathcal O(\alpha^6)$ $s, t, u$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to order $\mathcal O(\alphas \alpha^5)$  \\
        \hline
        \hline
        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
        {\sc Powheg}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & virt. No &  No \\
        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\
    \end{tabularx}
    \caption{\label{tab:wg1_codes} Summary of the different properties of the computer programs employed in the comparison.}
\end{table*}

### 2018-03-04 Draft/distributionsLO.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference of the two tagging jets (right) which are key observables for VBS measurements.
In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}.
For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as from non-resonant configurations are suppressed in the fiducial region.
In general, the agreement is at the level of $1\%$ or below for each bin.
We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, or transverse momentum.
This means that at LO, in the fiducial volume and for energies relevant to the LHC, the VBS approximation is good to a per cent.
This is in agreement with the findings of Sec.~\ref{subsec:LOinclusive} as the present comparison completely excludes the phase-space region where tri-boson contributions could have a noticeable impact.

 \begin{figure*}[htb!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/mjj_LO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/dyj1j2_LO.pdf}
\caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at LO accuracy and order $\mathcal{O}(\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\end{figure*}

>>>>

In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (left) and the rapidity difference of the two tagging jets (right) which are key observables for VBS measurements.
In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over the predictions of {\sc MoCaNLO+Recola}, 
for which we also display the scale-uncertainty band (seven-points variation).
For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as interferences are suppressed in the fiducial region.
In general, the agreement is at the level of $1\%$ or below in each bin.
We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, or transverse momentum.
This means that at LO, in the fiducial volume and for energies relevant to the LHC, the VBS approximation is good to a per cent.
This is in agreement with the findings of Sec.~\ref{subsec:LOinclusive} as the present comparison completely excludes the phase-space region where tri-boson contributions could have a noticeable impact.

 \begin{figure*}[htb!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/mjj_LO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/LO/dyj1j2_LO.pdf}
\caption{\label{fig:wg1_mjj-llLO} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right) at LO accuracy and order $\mathcal{O}(\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\end{figure*}
